Automated topic naming to support cross-project analysis of software maintenance activities

### 2011-01-25 msr/msr2011.tex
more intro edits

One challenge for software maintenance is to identify the reasons
behind software development activities. 
Identifying these reasons provides insight into \emph{why} certain
changes were made. 
Topic modeling is a machine learning technique which creates
multinomial distributions over words from a text corpus. 
The technique infers the hidden structure of a corpus using posterior
inference (the probability of the hidden structure given the data). 
Topic models are useful in software maintenance because they summarize
the key concepts in a corpus, such as source code, commit comments, or
email, by identifying statistically co-occurring words. 
Among other uses, it can quickly give developers an overview of where
activity occurred, and gives managers or maintainers a sense of
project history. 
For example, a topic extracted from a set of commit logs might be
\emph{ ``listener change remove add fire''}. 
A major challenge for topic modeling is to accurately identify the summary label for a topic (in the previous case, perhaps \emph{``event-handling''}). 
Current approaches are manual: they rely on human expertise to
recognize the appropriate label. 
Furthermore, to date the results of topic modeling are project
specific, and not generalizable. 
This paper presents an approach, \emph{labelled topic extraction}, which addresses these two problems.

>>>>

One challenge for software maintenance is to identify the reasons
behind software development activities. 
Identifying these reasons provides insight into \emph{why} certain
changes were made. 
Topic modeling is a machine learning technique which creates
multinomial distributions over words from a text corpus. 
The technique infers the hidden structure of a corpus using posterior
inference: the probability of the hidden structure given the data. 
Topic models are useful in software maintenance because they summarize
the key concepts in a corpus, such as source code, commit comments, or
mailing-list messages, by identifying statistically co-occurring words. 
Among other uses, it can quickly give developers an overview of where
activity occurred, and gives managers or maintainers a sense of
project history. 
For example, a topic extracted from a set of commit logs might be
\emph{ ``listener change remove add fire''}. 
A major challenge for topic modeling is to accurately identify the
summary label for a topic; in the previous case, perhaps
\emph{``event-handling''} would be appropriate. 
Current approaches are manual: they rely on human expertise to
recognize the appropriate label. 
Furthermore, to date the results of topic modeling are project
specific, and not generalizable. 
This paper presents an approach, \emph{labelled topic extraction}, which addresses these two problems.
